Adversarial State Aggregation

### 2019-10-29 minutia/paper/paper.tex
paper LSPI added

 \usepackage[sort]{natbib}

\title{Feature Extraction and Aggregation}

@@

\author{%
  Shayan Amani, Marek Petrik \\ %\thanks{Use footnote for providing further information
%    about author (webpage, alternative address)---\emph{not} for acknowledging
%    funding agencies.}%
  Department of Computer Science\\
  University of New Hampshire \\
  \texttt{\{shayan\}\{mpetrik\}@cs.unh.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\section{Introduction}

@@

\section{Definition}
For the sake of clarity, we elaborate on some preliminary definitions here to have a consistent set of notations to the end of this paper.

>>>>

\title{Adversarial State Aggregation}

@@

\author{%
Shayan Amani \\ %\thanks{Use footnote for providing further information
%    about author (webpage, alternative address)---\emph{not} for acknowledging
%    funding agencies.}%
Department of Computer Science\\
University of New Hampshire \\
\texttt{\{shayan\}\{mpetrik\}@cs.unh.edu} \\
% examples of more authors
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \AND
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
}

@@

    \section{Introduction}
    Although state aggregation may not generalize as well as methods based on neural networks, the techniques has
    both analytical and practical advantages. In camparison, state aggregation takes less computation power to
    compute representative features. Moreover, analysis and troubleshooting in a state aggregation process is more
    obvious than a black-box neural network. Approximation is a corner stone in all successfull RL methods to hold a
    "good" mapping between a large state space to a much smaller one where in value function is computable or at
    lesast feasible. These "good" approximators end up with "good" features to represent the projected state space.

@@

    \section{Method}
    For the sake of clarity, we elaborate on some preliminary definitions here to have a consistent set of notations
    to the end of this paper. We use model-free LSPI and LSTDQ \citep{Lagoudakis2003} to calculate and
    evaluate the policy of actions, respectively.
